a) summary of data sets
```{r}
data<-read.csv('heart.csv',header=TRUE)
help(data)
summary(data)
```


```{r}
head(data)
```
```{r}
age <- data[,1]
hist(age)
```
```{r}
sex <- data[,2]
hist(sex)
```
```{r}

cp <- data[,3]
hist(cp)
```
```{r}
trtbps <- data[,4]
hist(trtbps)
```
```{r}
chol <- data[,5]
hist(chol)
```
```{r}
fbs <- data[,6]
hist(fbs)
```

```{r}
restecg <- data[,7]
hist(restecg)
```
```{r}
thalachh <- data[,8]
hist(thalachh)
```
```{r}
exng <- data[,9]
hist(exng)
```
```{r}
oldpeak <- data[,10]
hist(oldpeak)
```
```{r}
slp <- data[,11]
hist(slp)
```
```{r}
caa <- data[,12]
hist(caa)
```
```{r}
thall <- data[,13]
hist(thall)
```
```{r}
outcome <- data[,14]
hist(outcome)
```

b) Apply all the outlier detection methods described above to your data set as they fit

-Statistical Tests based Approaches:
a) Dixon test (small sample size)

```{r}
X=data[1:30,3]
dixon.test(X,type=0,opposite=TRUE)
```

b) Normalscore 

```{r}
X=data[,2:4]
#scores(X,type="z",prob=0.95)
#Displaying first 10 scores
scores(X,type="z",prob=0.95)[1:10,]
```
c) Median Absolute Deviation (Deviation with respect to the median)
```{r}
X=data[,2:4]
#scores(X,type="mad",prob=0.95)
#Displaying first 10 scores
scores(X,type="mad",prob=0.95)[1:10,]
```
d) Interquantile range score
```{r}
X=data[,2:4]
#scores(X,type="iqr",lim=1)
#Displaying first 10 scores
scores(X,type="iqr",lim=1)[1:10,]
```
Depth-based Approach:
```{r}
X=data[,2:4]
depthout(X,cutoff=0.05)
```
Distance-based Approaches
a) Outlier detection using Mahalanobis Distance
```{r}
X=data[,2:4]
maha(X,cutoff=0.9)
```
b) Outlier detection using k Nearest Neighbours Distance method
```{r}
X=data[,2:4]
nn(X,k=4)
```

c) Outlier detection using kth Nearest Neighbour Distance method
```{r}
X=data[,2:4]
nnk(X,k=4)
```
Density-based Approaches
a) Outlier detection using Robust Kernal-based Outlier Factor(RKOF) algorithm

```{r}
X=data[,2:4]
dens(X,k=4,C=1)
```

b) Outlier detection using genralised dispersion
```{r}
X=data[,2:4]
disp(X,cutoff=0.99)
```
Join assessment of outlier detection methods using techniques described under 2 to 5.
```{r}
X=data[,2:4]
OutlierDetection(X, Method = "Euclidean", distance = TRUE, depth = TRUE)
```



